ISYE 6501

### 2022-10-19 hw8-1/Submission.Rmd
added hw8 submission.rmd

---
title: "ad_ques12.2"
author: "Ashish Dhiman"
date: "2022-10-19"
output: html_document
---

```{r}
library(FrF2)
```

@@

@@

>>>>

---
title: "ISYE 6501"
output:
  html_document:
    df_print: paged
  pdf_document: default
date: "2022-09-12"
---

# Submission HW8 \| Fall 22

-   Ashish Dhiman \| [ashish.dhiman\@gatech.edu](mailto:ashish.dhiman@gatech.edu){.email}

-   Abhinav Arun \| [aarun60\@gatech.edu](mailto:aarun60gatech.edu){.email}

-   Anshit Verma \| [averma373\@gatech.edu](mailto:averma373@gatech.edu){.email}

## Question 12.1

@@

```{r, include=FALSE}
library(FrF2)
```

@@

## Question 13.1

a.	**Binomial** - In finding defective items, the outcome could be either success (item is defective) or failure (item is non-defective).
b.	**Geometric** - For example, you ask people outside a polling station who they voted for until you find someone that voted for the independent candidate in a local election. The geometric distribution would represent the number of people who you had to poll before you found someone who voted independent. You would need to get a certain number of failures before you got your first success.
c.	**Poisson** - It gives the probability of an event happening a certain number of times (k) within a given interval of time or space. One example is no. of website visitors per month.
d.	**Exponential** - One example is the amount of time, in months, a car battery lasts.
e.	**Weibull** - One example is Warranty analysis. We are using data to model time-to-failure.
